%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.
%
% https://math.berkeley.edu/~vojta/tex/ucbthesis-phd.html

\documentclass{ucbthesis}
\usepackage[dvipdfmx]{graphicx} % needs to be up top
\usepackage{bmpsize}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[sorting=none,backend=biber]{biblatex}
\usepackage{color}
\usepackage{etoolbox}
\usepackage[hidelinks]{hyperref}
\usepackage[super]{nth}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{3d,angles,quotes,calc}
\usepackage[export]{adjustbox} % must be below tikz else tikzplots are scronched
\usepackage[version=3]{mhchem}
\usepackage{textcomp}
\usepackage{stmaryrd} % for short right arrow
\usepackage{placeins}
\usepackage{multirow}
\usepackage{subcaption}

\newcommand{\sa}{\shortrightarrow}
\newcommand{\bo}{\mathbf\Omega}
\newcommand{\vecr}{\textbf{r}}
\newcommand{\sn}{S$_\mathrm{N}$~}
\newcommand{\pn}{P$_\mathrm{N}$~}
\newcommand{\sigt}{\Sigma_t}
\newcommand{\sigs}{\Sigma_s}
\newcommand{\hl}{\mathcal{H}_L}
\newcommand{\maths}{\mathbb{S}^2}
\newcommand{\dl}{d_L}
\newcommand{\lij}{\langle L_i,L_j \rangle}
\newcommand{\kij}{\langle K_i,K_j \rangle}
\newcommand{\ve}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\Ye}[2]{\ensuremath{Y^e_{#1}(\bo_#2)}}
\newcommand{\Yo}[2]{\ensuremath{Y^o_{#1}(\bo_#2)}}
\newcommand{\Sigg}[1]{\ensuremath{\Sigma^{g'\sa g}_{\text{s},#1}}}
\newcommand{\even}{\ensuremath{\phi^g}}
\newcommand{\odd}{\ensuremath{\vartheta^g}}
\newcommand{\xhat}{\ensuremath{\hat{x}}}
\newcommand{\xbar}{\ensuremath{\bar{x}}}
\newcommand{\qhat}{\ensuremath{\hat{q}}}
\newcommand{\psihat}{\ensuremath{\hat{\psi}}}
\newcommand{\khat}{\ensuremath{\hat{K}}}
\newcommand{\Gij}[2]{\sum_{\ell=0}^L\frac{2\ell+1}{4\pi}P_{\ell}(\bo_#1\cdot\bo_#2)}
\newcommand{\Sij}[2]{\Sigma^{g'\rightarrow g}_{\text{s,L}}(\bo_#1\cdot\bo_#2)}
\newcommand{\Snij}[3]{\Sigma^{g'\rightarrow g}_{\text{s,#1}}(\bo_#2 \cdot \bo_#3)}
\newcommand{\Snz}[3]{\Sigma^{0\sa 0}_{\text{s,#1}}(\bo_#2 \cdot \bo_#3)}
\newcommand{\ldosig}[2]{\sum_{n=0}^N \frac{2n+1}{4\pi}\sigma_{s,n}^{g'\rightarrow g} P_n(\bo_#1\cdot\bo_#2)}
\newcommand{\fq}{\qquad\qquad\qquad\qquad}
\newcommand{\st}{\tilde{S}}
\newcommand{\E}[1]{$\times10^{#1}$}
\newcommand{\del}{\partial}
\newcommand{\mr}[1]{\multirow{2}{*}{#1}}

\makeatletter
\let\oldcite\cite
\pretocmd{\listoffigures}{\def\cite{\ignorespaces\@gobble}}{}{}
\apptocmd{\listoffigures}{\let\cite\oldcite}{}{}
\makeatother

\makeatletter
\let\oldcite\cite
\pretocmd{\listoftables}{\def\cite{\ignorespaces\@gobble}}{}{}
\apptocmd{\listoftables}{\let\cite\oldcite}{}{}
\makeatother

% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\newtheorem{theorem}{Jibberish}

\bibliography{references}

\hyphenation{mar-gin-al-ia}
\hyphenation{bra-va-do}
\hyphenation{quad-ru-ple}
\hyphenation{ADVANTG}
\hyphenation{CADIS}
\newcommand{\fwc}{\mbox{FW-CADIS}}
\newcommand{\co}{\mbox{CADIS-$\Omega$}}
\newcommand{\fwco}{\mbox{FW/CADIS-$\Omega$}}

\begin{document}

% Declarations for Front Matter

\title{Advanced Quadrature Selection for Monte Carlo Variance Reduction}
\author{Kelly L. Rowland}
\degreesemester{Spring}
\degreeyear{2018}
\degree{Doctor of Philosophy}
\chair{Assistant Professor Rachel N. Slaybaugh}
\othermembers{
	Associate Professor Per-Olof Persson \\
	Professor Jasmina Vuji\'c \\
	Dr. Steven P. Hamilton
	}
\numberofmembers{4}
\field{Engineering -- Nuclear Engineering}
% Designated Emphasis -- this is optional, and rare
\emphasis{Computational and Data Science and Engineering}
\campus{Berkeley}

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
% \approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

% to show paragraphs in ToC (good for an outline, stylistically ugly):
% \setcounter{secnumdepth}{4}
% \setcounter{tocdepth}{4}

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}
\small
It takes a village to make a doctor. I cannot express how grateful I am to
the colleagues, friends, family, and various community members who have
supported me throughout my tenure in graduate school. Without all of your
contributions, this process would have been much more difficult.

Many thanks go to my dissertation committee for their time and effort spent
in improving the quality of this writing. I would like to thank the Exnihilo
team at Oak Ridge National Laboratory for all of their help and guidance.
Dr. Steven Hamilton, you have my sincerest gratitude for your help at all
levels of this project, from working through big conceptual questions to
kindly pointing out the smallest of floating point errors. This work would
not have been finished in any sort of timely manner without your generosity.

My colleagues have made Berkeley an amazing place to work and grow. Drs.
Phil Gorman and Katy Huff, thank you for your patience and kindness in
teaching me scientific computing skills when I had none. Dr. Madicken Munk,
my commiserator-in-chief, thank you for seeing me through the most trying
of times and for paving a better-informed \texttt{PATH} than I would have
otherwise traversed. Daniel Wooten, thank you for helping me to say no
to more things. Josh Rehak, thanks for helping me keep it surreal. Ellen
Edwards, thank you for continually inspiring me to challenge myself.

Berkeley Research Computing has been a great source of pride and joy for me
to be a part of. Aaron Culich, I cannot thank you enough for looking at a
graduate student in desperate need of help and seeing the potential for so
much more. I am grateful to the Department of Nuclear Engineering for all of
the free coffee that it has provided.

To my family, thank you for your endless support and encouragement. You have
provided me with an incredible foundation from which I have been fortunate
to pursue any and all of my dreams.

Cathy Berman, thank you for being my personal cheerleader and helping me
grow into myself. Dr. Dillon Shaver, thank you for helping me pass my
screening exams when I really needed it.
Shola Ogunlana, thank you for leading the STRONGER family
to be better versions of ourselves through each and every burpee. Mitch
Crispell, thank you for bringing joy to every single person who steps into
one of your dance classes. Alex Converse, thank you for the love and support
that you have provided, even when it meant bearing with me through a few
periods of crunch time.

Professor Rachel N. Slaybaugh, thank you for advising me in so much more
than just this dissertation work. Your perspective and insights have helped
me to not only bloom as a researcher, but to a grow as a person as well. I
am very fortunate to have had your support in the myriad of endeavors that
I have undertaken in graduate school. Thank you for caring about my well-being
as an individual and broadening my horizons in ways that I never could have
fathomed.

\vspace{\fill}

\scriptsize{This material is based upon work supported under an Integrated
University Program Graduate Fellowship as well as supported by the Department 
of Energy under Award Number(s) DE-NE0008661. This report was prepared as an account 
of work sponsored by an agency of the United States Government. Neither the United 
States Government nor any agency thereof, nor any of their employees, makes any 
warranty, express or limited, or assumes any legal liability or responsibility for the 
accuracy, completeness, or usefulness of any information, apparatus, product, or
process disclosed, or represents that its use would not infringe privately owned
rights. Reference herein to any specific commercial product, process, or service by
trade name, trademark, manufacturer, or otherwise does not necessarily constitute or
imply its endorsement, recommendation, or favoring by the United States Government or
any agency thereof. The views and opinions of authors expressed herein do not 
necessarily state or reflect those of the United States Government or any agency 
thereof. This research used the Savio computational cluster resource provided by the 
Berkeley Research Computing program at the University of California, Berkeley 
(supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief 
Information Officer).}

\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

% (Optional) \part{First Part}

\include{intro}
\include{background}
\include{method}
\include{results}
\include{conclusion}

\def\StripPrefix#1>{}
\def\jobis#1{FF\fi
  \def\predicate{#1}%
  \edef\predicate{\expandafter\StripPrefix\meaning\predicate}%
  \edef\job{\jobname}%
  \ifx\job\predicate
}

\if\jobis{thesis}
  \printbibliography
\else
  \newpage
  \renewcommand{\thepage}{}
  \printbibliography
\fi

%\appendix
% \include{mathbg}

\end{document}
